Active Object Search with a Mobile Device for the Visually Impaired

### 2018-11-23 paper.tex

>>>>

The position of the waypoint is given to the user by a set of guidance instructions (the arrows seen on-screen in Figure~\ref{fig:system-screenshot}) in terms of the actions defined in $\textbf{A}$. This might seem like an unnecessary extra step, but this system is designed for VI users who are limited to audio instructions, which makes it necessary to split the instructions up into separate channels that can be communicated more simply. This requirement becomes clear when one considers the bandwidth limitations of a human's audio channel as compared to the visual one.
